A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-04-24 paper.tex
Changed interpolate example to controller moves

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [left] {$b$}
                    }
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] (n) {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {$e$}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {$f$}
                    }
                    edge from parent [fixed] {node [right] {$d$}}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
            \node [right=1pt of n] {$n$};
        \end{tikzpicture}
        \caption{A losing AGT $T$}
        \label{fig:interpolatetree}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [left] {$b$}
                    }
                    edge from parent [fixed] node [left] {$a$}
                }
                child {node [circle,draw] (n) {}
                    edge from parent [fixed] node [right] {$d$}
                }
                node [above=4pt] {$\langle s, 2 \rangle$};
            \node [right=1pt of n] {$n$};
        \end{tikzpicture}
        \caption{Tree slice $T_1$}
        \label{fig:treef1}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] {}
                child {node [circle,draw,right=5pt] {}
                    edge from parent [fixed] node [left] {$e$}
                }
                child {node [circle,draw,left=5pt] {}
                    edge from parent [fixed] node [right] {$f$}
                }
                node [right=5pt] {$n$};
        \end{tikzpicture}
        \caption{Tree slice $T_2$}
        \label{fig:treef2}
    \end{subfigure}
    \caption{Splitting of an abstract game tree by the learning procedure.}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \begin{subfigure}[t]{.32\textwidth}
        \centering

        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    child {node [circle,draw,right=5pt] {}
                        edge from parent [fixed] node [left] {\texttt{gr0=1, gr1=0}}
                    }
                    child {node [circle,draw,left=5pt] {}
                        edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                    }
                    node [left=5pt] {$n$}
                    edge from parent [fixed] node [left] {\texttt{gr0=0, gr1=1}}
                }
                child {node [circle,draw] (n) {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                    }
                    edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                }
                node [above=4pt] {$\langle s, k \rangle$};
        \end{tikzpicture}
        \caption{A losing AGT $T$}
        \label{fig:interpolatetree}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] (root){}
                child {node [circle,draw] {}
                    node [left=5pt] {$n$}
                    edge from parent [fixed] node [left] {\texttt{gr0=1, gr1=0}}
                }
                child {node [circle,draw] (n) {}
                    child {node [circle,draw] {}
                        edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                    }
                    edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                }
                node [above=4pt] {$\langle s, k \rangle$};
        \end{tikzpicture}
        \caption{Tree slice $T_1$}
        \label{fig:treef1}
    \end{subfigure}%
    \begin{subfigure}[t]{.32\textwidth}
        \centering
        \begin{tikzpicture}[dash pattern = on 2pt off 2pt, level distance = 10mm]
            \node [circle,draw] {}
                child {node [circle,draw,right=5pt] {}
                    edge from parent [fixed] node [left] {\texttt{gr0=1, gr1=0}}
                }
                child {node [circle,draw,left=5pt] {}
                    edge from parent [fixed] node [right] {\texttt{gr0=1, gr1=1}}
                }
                node [left=5pt] {$n$};
        \end{tikzpicture}
        \caption{Tree slice $T_2$}
        \label{fig:treef2}
    \end{subfigure}
    \caption{Splitting of an abstract game tree by the learning procedure.}
\end{figure}
